Exploring probability distributions for bivariate temporal granularities

### 2019-11-03 main.Rmd
revising subsections for visualization section

<!-- Lit review on statistical distribution plot-->
## Statistical distribution plots

@@

## Plotting harmonies and clashes

## Homogeneity across and within facets

 -  very high facet and x-axis levels

 X-axis variable is treated as a categorical variable and hence any plots which

suppose we have $T$ hourly observations, and $C_1$ is HOD and $C_2$ is DOW. Each element of $C_1$ occurs approximately $T/n_1$ times while each element of $C_2$ occurs approximately $T/n_2$ times. There are no structurally empty combinations, and each combination will occur on average an equal number of times as $T\rightarrow\infty$, so the average number of observations per combination is $T/(n_1n_2)$. If we require at least $k$ observations to create a meaningful panel, then provided $T \ge n_1n_2k$, the visualization will be acceptable. The value of $k$ will depend on what type of visualization we are producing. For scatterplots, even $k=3$ may be acceptable, but for density estimates, we probably need $k \ge 30$.

## Number of levels of the facet variable

@@

```{r}

>>>>

## Choice of Plots

<!-- Graphical output devices are flat. If there are only two variables, a cartesian graph of one variable against the other can show the configuration of points. As soon as the data move to three variables, we must be content in attempting to infer multi-dimensional structure by a two-dimensional medium.  -->

Facetting creates small multiples of data each representing a different subset of the data. Small multiples are powerful for exploratory data analysis where we can rapidly compare patterns in different parts of the data and see whether they are the same or different. But space and resolution quickly become a problem if the number of levels of facet variables is too high. Also, Cleveland suggested that a graphic should display as much information as it can, with the lowest possible cognitive strain to the viewer.

## Effect of interaction

We should avoid plotting clashes as they hinder the exploratory process by having missing combinations of time granularities in each panel.

## Effect of number of observation

### Rarely occuring events

Suppose we have $T$ hourly observations, and $C_1$ is HOD and $C_2$ is DOW. Each element of $C_1$ occurs approximately $T/n_1$ times while each element of $C_2$ occurs approximately $T/n_2$ times. There are no structurally empty combinations, and each combination will occur on average an equal number of times as $T\rightarrow\infty$, so the average number of observations per combination is $T/(n_1n_2)$. If we require at least $k$ observations to create a meaningful panel, then provided $T \ge n_1n_2k$, the visualization will be acceptable. The value of $k$ will depend on what type of visualization we are producing. For scatterplots, even $k=3$ may be acceptable, but for density estimates, we probably need $k \ge 30$.

### Homogeneity within and across facets

We should be cautious to plot two granularities which vary largely across or within facets. Even if for each combinations, the number is good enough for plotting distribution, large differences between number of observations between and across facets, might have an impact on the emperical dfistribution. We use Gini's measure to compute if differences in number of observations across or within facets are significantly different.

<!-- Lit review on statistical distribution plot-->
 Statistical distribution plots

@@

Recommendation system that aid exploration

@@
